### 2019-11-07 report/paper.tex
add comparison

\subsection{Results}\label{subsec:results}
Present the results, both qualitatively (visualize) and quantitatively (specific numbers)..
Analyze the results

\begin{figure}[]
    \centering
    \begin{subfigure}{0.6\linewidth}
    \begin{tabular}{lcccc}
        \toprule
        class & precision & recall & \( F_1 \) score & \#samples \\
        \midrule
           waldo &  1.00 &  0.69 & 0.82 &  13 \\
           wenda &  0.80 &  0.57 & 0.67 &   7 \\
          wizard &  0.00 &  0.00 & 0.00 &   3 \\
        negative &  0.69 &  1.00 & 0.82 &  20 \\
        \bottomrule
    \end{tabular}
    \end{subfigure}
    \begin{subfigure}{0.35\linewidth}
    \includegraphics[width =\linewidth]{figures/confusion_matrix}
    \end{subfigure}

    \caption{Classification accuracies for waldo, wenda, wizard and negative classes on the HOG/HOV and SVM classifier
    with confusion matrix between the classes to the right.}
    \label{tab:classification_acc}
\end{figure}
\begin{table}
    \centering
    \begin{tabular}{lccccc}
        \toprule
        method & \( I_1 \) IoU & \( I_2 \) IoU & \( I_3 \) IoU & Mean IoU & Mean Time \\
        \midrule
        % Histogram correlation   & 0.8   & 0.8 & 0.8 & 1s \\
        HOG \& SVM              & 0.0   & 0.0 & 0.37 & \textbf{0.13} & 12.8 s \\
        HOG/HOV \& SVM          &  0.0  & 0.5 & 0.09 & \textbf{0.21} & 21.3 s \\
        \bottomrule
    \end{tabular}
    \caption{Comparison over cropped image regions (see \autoref{fig:detections}). Given is IoU with the ground truth bounding box for each image,
    as well as mean computation time.}
    \label{tab:class-iou}
\end{table}
\begin{figure}
    \centering
    \begin{subfigure}{0.3\linewidth}
    \stackunder[5pt]{\includegraphics[height=4.5cm]{figures/crop_1}}{Wizard image: \( I_1 \)}
    \end{subfigure}
    \begin{subfigure}{0.3\linewidth}
    \stackunder[5pt]{\includegraphics[height=4.5cm]{figures/crop_2}}{Wenda image: \( I_2 \)}
    \end{subfigure}
    \begin{subfigure}{0.3\linewidth}
    \stackunder[5pt]{\includegraphics[height=4.5cm]{figures/crop_3}}{Waldo image: \( I_3 \)}
    \end{subfigure}
    \caption{Cropped wizard, wenda and waldo images \( I_1, I_2, I_3 \) with ground truth bounding boxes marked in green, detections in red.
    Every cropped image only contains only one ground truth annotation.}
    \label{fig:detections}
\end{figure}

\begin{equation*}
    \text{precision} = \frac{|TP|}{|TP| + |FP|}  
    \quad
    \text{recall} = \frac{|TP|}{|TP| + |FN|}
    \quad
    F_1 = 2\cdot \frac{\text{precision} \cdot \text{precall}}{\text{precision} + \text{recall}}
\end{equation*}

Evaluate hog only vs hog / hov
\subsection{Discussion}
Strengths and weakness in your method.

@@

Looking at the results our classifier produced for the test images, it appears that the internal
representation of our classes is not distinctive enough to achieve a very good classification performance.
An example for a classification error that undergirds this hypothesis can be seen in TBD

\section{Conclusion}
In this project, we useed several computer vision techniques and algorithms that we had
learnt in class, and put them into practice. Though our solution needs further work on the dismissal of
false positives, we manage to detect several instances of the characters of interest. By trying several
classification approaches simultaneously in the beginning of the project phase, we were able to reject those
which were less promising and could therefore concentrate our energy on improving the algorithm providing
the best results. The pursue of the idea to combine two feature descriptors lead to a significant increase
of the average performance of our classifier.

\section{Group Information}

\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& Axx & e0445541@u.nus.edu & xxx \\
    David Drews& Axx &e0454245@u.nus.edu & xxx  \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & xxx  \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}

>>>>

\subsection{Results}\label{subsec:results}

\begin{figure}[]
    \centering
    \begin{subfigure}{0.6\linewidth}
    \begin{tabular}{lcccc}
        \toprule
        class & precision & recall & \( F_1 \) score & \#samples \\
        \midrule
           waldo &  1.00 &  0.69 & \textbf{0.82} &  13 \\
           wenda &  0.80 &  0.57 & \textbf{0.67} &   7 \\
          wizard &  0.00 &  0.00 & \textbf{0.00} &   3 \\
        negative &  0.69 &  1.00 & \textbf{0.82} &  20 \\
        \bottomrule
    \end{tabular}
    \end{subfigure}
    \begin{subfigure}{0.35\linewidth}
    \includegraphics[width =\linewidth]{figures/confusion_matrix}
    \end{subfigure}

    \caption{Classification accuracies for waldo, wenda, wizard and negative classes on the HOG/HOV and SVM classifier
    with confusion matrix between the classes to the right.}
    \label{tab:classification_acc}
\end{figure}

% Present the results, both qualitatively (visualize) and quantitatively (specific numbers)..
% Analyze the results
Our Evaluation was is twofold, as we will firstly cover just the HOG/HOV \& SVM classifier itself, as evaluated on the 
validation set provided and then discuss how these results transfer over to the more general problem of detecting the classes in
full images.

For evaluation we use the now standard metrics in computer vision of precision, recall and their harmonic average the \( F_1 \) score.
They are defined as follows:

\begin{equation*}
    \text{precision} = \frac{|TP|}{|TP| + |FP|}  
    \quad
    \text{recall} = \frac{|TP|}{|TP| + |FN|}
    \quad
    F_1 = 2\cdot \frac{\text{precision} \cdot \text{precall}}{\text{precision} + \text{recall}}
\end{equation*}
Where \( TP \) is the set of \textbf{true positives}, intuitively detections of waldo, wenda, wizard or negative, which are also marked 
as the \textit{same} class in the validation set. 
\( FP \) is the set of \textbf{false positives}, intuitively cases where the detection is marked as the class under consideration, but actually belongs to any of the other ones.
\( FN \) is the set of \textbf{false negatives}, intuitively detections considered to be one of the classes other then the one under consideration, but which do belong to that class.

Considering the results achieved by the HOG/HOV \& SVM classifier on the validation set, 
we can see in \autoref{tab:classification_acc} that \( F_1 \) scores for the classes waldo and negatives are quite high, with
their precision and recall scores being opposites of each other. This suggests, that even although we trained a multiclass classifier, 
it is effectively classifying between the waldo and negative classes. This assumption also holds further when looking at the other
\( F_1 \) scores for wenda and wizard. They are acceptable for wenda, but none of the testing examples were classified as wizard, 
showing how our classifier is very unlikely to correctly detect wizard windows, which we will also discuss in the following paragraphs.

Gengeralizing our classifier to multiclass detector, we will now consider cropped images showing one ground truth class per image. 
Exemplary we have chosen three images to analyse from the dataset in \autoref{fig:detections}.
Already in the images one can see that overlap between the ground truth bounding boxes and the detections is not always large.
This is especially the case for \( I_1 \) containing wizard images, where the detected bounding box for wizard looks similar to the
ground truth box but is still a miss. We claim this could be classified as a close miss, hinting at a larger problem present in the dataset, 
of there being many possible windows which look very similar to true detections but are still considered negative even to the human eye. 
However the detections for \( I_2, I_3 \) are closer to the ground truth.

\begin{figure}
    \centering
    \begin{subfigure}{0.3\linewidth}
    \stackunder[5pt]{\includegraphics[height=4.5cm]{figures/crop_1}}{Wizard image: \( I_1 \)}
    \end{subfigure}
    \begin{subfigure}{0.3\linewidth}
    \stackunder[5pt]{\includegraphics[height=4.5cm]{figures/crop_2}}{Wenda image: \( I_2 \)}
    \end{subfigure}
    \begin{subfigure}{0.3\linewidth}
    \stackunder[5pt]{\includegraphics[height=4.5cm]{figures/crop_3}}{Waldo image: \( I_3 \)}
    \end{subfigure}
    \caption{Cropped wizard, wenda and waldo images \( I_1, I_2, I_3 \) with ground truth bounding boxes marked in green, 
    detections by HOG/HOV \& SVM in red with associated \( p, p_{ratio} \) values.}
    \label{fig:detections}
\end{figure}
\begin{table}
    \centering
    \begin{tabular}{lccccc}
        \toprule
        method & \( I_1 \) IoU & \( I_2 \) IoU & \( I_3 \) IoU & Mean IoU & Mean Time \\
        \midrule
        % Histogram correlation   & 0.8   & 0.8 & 0.8 & 1s \\
        HOG \& SVM              & 0.0   & 0.0 & 0.37 & \textbf{0.13} & 12.8 s \\
        HOG/HOV \& SVM          &  0.0  & 0.5 & 0.09 & \textbf{0.21} & 21.3 s \\
        \bottomrule
    \end{tabular}
    \caption{Comparison over cropped image regions (see \autoref{fig:detections}). Given is IoU with the ground truth bounding box for each image,
    as well as mean computation time.}
    \label{tab:class-iou}
\end{table}

\subsection{Discussion}
Strengths and weakness in your method.

@@

\section{Conclusion}
In this project, we managed to make use of several computer vision techniques and algorithms that we had learnt in class, and put them into practice. Although the results are not perfect, with the presence of several false positives, we managed to be able to detect some instances of the characters using our proposed solution. Which, given the timeline and schedule, is quite an achievement in its own.

\section{Group Information}
\begin{table*}[ht]
    \centering
    \begin{tabular}{lccc}
    \toprule
     Member & Student ID & Email & Contribution\\
    \midrule
    Maximilian Fruehauf& Axx & e0445541@u.nus.edu & xxx \\
    David Drews& Axx &e0454245@u.nus.edu & xxx  \\
    Choo Wen Xin& A0160465H & e0053347@u.nus.edu & xxx  \\
    \bottomrule
    \end{tabular}
    \caption{Group member information.}
    \label{tab:dataset}
\end{table*}
